Supplementary Information

### 2021-02-18 doc/manuscript/ForestGEO_treerings_SI.Rmd
some changes from Jim Lutz
Update ForestGEO_treerings_SI.Rmd

### Cedar Breaks, Utah, USA
Cores were collected within the Utah Forest Dynamics Plot ForestGEO plot on the Colorado Plateau in Cedar Breaks National Monument [CB; @furniss_reconciling_2017]. 
The plot sits on the edge of cliff, which descends ~750 m to a valley below.
The mature spruce-fir forest is dominated by the species analyzed here (*Abies bifolia*, *Populus tremuloides*, *Picea engelmannii*, *Pinus flexilis*, *Pinus longaeva*, *Picea pungens*, and *Pseudotsuga menziesii*).
The site is largely undisturbed. 
The most recent fire occurred in 1802, and many currently living trees established before then. Living *Pinus longaeva* at the site date back ~1600 years, and deadwood at the site dates back to 0 AD (Cooper & Lutz, unpublished data).

@@

[ISSUE #25 in ForestGEO-climate-sensitivity ](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/25)

>>>>

### Cedar Breaks, Utah, USA
Cores were collected within the Utah Forest Dynamics Plot ForestGEO plot on the Colorado Plateau in Cedar Breaks National Monument [CB; @furniss_reconciling_2017]. 
The plot sits on the edge of cliff, which descends ~750 m to a valley below.
The mature spruce-fir forest is dominated by the species analyzed here (*Abies bifolia*, *Populus tremuloides*, *Picea engelmannii*, *Pinus flexilis*, *Pinus longaeva*, *Picea pungens*, and *Pseudotsuga menziesii*).
The site is largely undisturbed. 
The most recent fire occurred in 1802, and many currently living trees established before then. Living *Pinus longaeva* at the site date back ~1600 years, and deadwood at the site dates back to 0 AD [@lutz_large-diameter_2021].

@@
